Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-22 analysis/paper/paper.Rmd
Clarify writing

When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores with a mean of zero.

>>>>

When predicting the availability of computational methods (code) and availability, all journals were compared with *Phytopathology* as the reference with latent scores having a mean of zero.
